Make any stupid plot you want

### 2020-12-30 draft/sections/math.tex
start of scratching out \nu

\subsubsection{Visual Channels}

A monoid is a set with a closed operation

The function $\nu: E \rightarrow V$ is a mapping from the data bundle to the visual bundle 
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "f"'] & V_i \arrow[d, "f"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}

such that a visual section $\mu: K \rightarrow V$  is equivalent to the visual transformation of the data $\mu(k) = \nu\circ\tau(k)$

The Stevens measurement scales\cite{stevensTheoryScalesMeasurement1946,leaFormalizationMeasurementScale} are examples of some of the group actions th

+2 on data side means +2 on visual side

.2 = E1 - lambda e -> .2 V1 = .2
+.2                              +.2
.4 = E2 - lambda e -> .2 V2 = .2

.2 = E1  - lambda e-> .2 V1 = .2

                        V2 = .2

1 = E1 - lambda e->e/5 = .25

+ 1                      +.25

2 = E2 - lambda e->e/5 = .5

preserve unique mapping? does $\nu$ need to be invertable?

shifts in either space need to be mirrored in the other space, this is not valid  here's why:
$\lambda e: .2$ 
\begin{equation}
    \label{eq:nu_equation_bad}
    \begin{tikzcd}
        E_1 \arrow[r] \arrow[r, "\lambda:e\mapsto.5"] \arrow[d, "e+2"'] & V_1 \arrow[d, "h+2"] \\
        E_2 \arrow[r, "\lambda"]                                        & V_2                 
    \end{tikzcd}
\end{equation}

{x,y} = {1,2}
{y,x} = {2,1}
{y,x} = {1,2}

>>>>

\subsubsection{Visual Channels}
$\nu: \tau \mapsto \mu$ is an equivariant map such that there is a homomorphism from monoid actions on $E_{i}$ to manoid actions on $V_{i}$  
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "f"'] & V_i \arrow[d, "f"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
where the diagram commutes such that  $\nu g(\tau_{i}) = g(\nu(tau_{i})$. Manoid actions are:
1) set of functions including identity, composition operator, closed, associative

To construct a valid $\nu$:
\begin{enumerate}
    \item identify monoid actions on $E_i$
    \item choose $V_i$ that can support same monoid actions
    \item implement $\nu$ such that composition holds
\end{enumerate}

\paragraph{Example: Translation}
When $tau_{i}$ of $E_1$ returns interval data, Steven's defines the group actions on the data as the general linear group \cite{stevensTheoryScalesMeasurement1946,leaFormalizationMeasurementScale}; therefore to construct a valid $\nu$, we choose a target variable in $P$ that is

$\nu_i(\tau_i) = \tau + 2$

$\lambda e: .2$ 
\paragraph{Example: Invalid $\nu$}
shifts in either space need to be mirrored in the other space, this is not valid  here's why:
\begin{equation}
    \label{eq:nu_equation_bad}
    \begin{tikzcd}
        E_1 \arrow[r] \arrow[r, "\lambda:e\mapsto.5"] \arrow[d, "e+2"'] & V_1 \arrow[d, "h+2"] \\
        E_2 \arrow[r, "\lambda"]                                        & V_2                 
    \end{tikzcd}
\end{equation}

\paragraph{Example: Partial Order}
$\nu$ induces a monoid homomorphism, rather than a group homomorphism, to allow for partial ordering. For example if E1 is the set '{}
